Initial Analysis

### 2019-08-21 Initial_Analysis.Rmd
Changed result path for all models file and included a n_core variable to determine number of cores used in computaion

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
  Path <- paste(Data_Path,sep = "")
}else{
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}

@@

Mclapply_Hack <- function(...){
    ## Create a cluster
    size.of.list <- length(list(...)[[1]])
    cl <- makeCluster(min(size.of.list, detectCores()))

@@

# For Function
Exploited_Species_List <- Exploited_Species$TaxonKey[1:3]

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
  Path <- paste(Data_Path,sep = "")
}else{
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
}

@@

Mclapply_Hack <- function(...){
    ## Create a cluster
    size.of.list <- length(list(...)[[1]])
    n_cores <- detectCores()-6
    cl <- makeCluster(min(size.of.list, n_cores))

@@

# For Function
Exploited_Species_List <- Exploited_Species$TaxonKey
